Ecuador plant species BIEN data

### 2022-10-10 code/L0/L0_1_Ecuador_plants_BIEN.Rmd
update top header information

---
title: "Ecuador plant species list"
authors: "Hazel Anderson"
collaborators: "None"
data input: "PlantsOfTheWorldOnline_Ecuador_species.xlsx and GBIF_Ecuador_PlantSpeciesList.csv"
data output: "Ecuador_unique_species_list.csv"
project: "Frugivoria"
date: "2022-08-17"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

>>>>

---
title: "Ecuador plant species BIEN data"
authors: "Hazel J. Anderson"
collaborators: "None"
data input: "none"
data output: "Ecuador_BIEN_species_list.csv, Ecuador_BIEN_occurrence.csv, Ecuador_BIEN_traits.csv"
project: "Frugivoria"
date: "2022-08-17"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```
